troubleshooting

### 2024-10-01 README.Rmd
0.99.2

Lastly, mspms takes advantage of iceLogos ([Colaert, N. et al. Nature Methods 6,
786-787 (2009)](http://www.ncbi.nlm.nih.gov/pubmed/19876014)) to viusalize
overrepresented amino acid motifs relative to a background set by implementing
components of the Java software in R.

@@

To generate a general report using your own data, run the following code. It
requires data that has been prepared for mspms data analysis by a converter
function, and a design matrix. For more information see subsequent sections.

>>>>

Lastly, mspms takes advantage of iceLogos ([Colaert, N. et al. Nature Methods 6,
786-787 (2009)](http://www.ncbi.nlm.nih.gov/pubmed/19876014)) to visualize
over-represented amino acid motifs relative to a background set by implementing
components of the Java software in R.

@@

To generate a general report using your own data, run the following code. It
requires data that has been prepared for mspms data analysis by a converter
function. For more information see subsequent sections.
